---
title: "wine"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#loading required libraries and dataset
```{r}
library(dplyr)
library(ggplot2)
library(gridExtra)
library(stringr)
library(tidyr)
library(httr)
library(jsonlite)
library(lubridate)
library(car)
library(effects)
library(SnowballC)
library(wordcloud)
library(tree)
library(caret)

#reading the data
wine <- read.csv("C:/Users/Administrator/Desktop/wine-reviews/winemag-data-130k-v2.csv")

#summary of the entire data
nrow(wine)
colnames(wine)

```

#to understand the data.By looking into "Description", we find that it is a factor with 119,955 levels, which is 10,016 less than the number of total records within the dataset. This shows us that there are some repeated values.
```{r}
wine$description %>% 
  glimpse()
```

#. Now we can proceed to get rid of the duplicates. We use a column named duplicate in order to tag those rows to delete, and drop the column once we are done.
```{r}
#duplicates
wine <- wine %>% 
  mutate(duplicate = duplicated(description)) %>% 
  filter(duplicate==FALSE) %>% 
  select(-duplicate) 


```

#create a table and a graph to analyze the distribution of reviews per country.
```{r}
wineCtry <- wine %>% 
  group_by(country) %>% 
  summarise(total = n()) %>% 
  arrange(desc(total)) %>% 
  mutate(totpcnt = round(total/ sum(total), digits=7), accum = cumsum(totpcnt))

wineCtry
```

#getting top 10 countries and plotting them 
```{r}
wineCtry %>% head(10) %>%
  ggplot( aes(x= factor(country, levels = wineCtry$country[order(desc(wineCtry$totpcnt))]), y = total)) +
  geom_col() + 
  geom_text(aes(label = sprintf("%.1f %%", 100*totpcnt), y = total + 1500)) +
  labs(x="Country", y="Total Reviews", title="Distribution of Wine Reviews by Top 10 Countries")
```


#quality over quantity graph
```{r}
wineRating = wine %>% 
 group_by(country) %>%
 summarise_at(vars(points), funs(points = mean(., na.rm=T))) %>%
 arrange(desc(points)) %>%
 head(10)

ggplot(data=wineRating, aes(x=reorder(country,-points), y= points)) + 
  geom_bar(stat="identity", fill = "navy") + 
  coord_cartesian(ylim=c(85,92)) + 
  labs(x="Countries", y="Rating", title="Top 10 Countries by Average Rating")
```


```{r}
wine %>%
  filter(country=="England") %>%
  summarize(count = n())
```

```{r}

wine %>%
 select(country, price) %>%
 group_by(country) %>%
 summarise(maxprice = max(price, na.rm = TRUE)) %>%
 arrange(desc(maxprice)) %>%
 head(10)
```

```{r}
t.test(wine$price[wine$country=="US"],
      wine$price[wine$country=="France"], paired=FALSE)
```

```{r}
#Group by taster and sort by total reviews. Analyze reviews distribution
wineTstr <- wine %>% group_by(taster_name) %>% summarise(total=n()) %>% 
  arrange(desc(total)) %>% 
  mutate(totpcnt = round(total/ sum(total), 7), accum = cumsum(totpcnt))

```

```{r}
#Factor the taster name on desc order for organizing the bars on the next plot
wineTstr$taster_name <- factor(wineTstr$taster_name, levels = wineTstr$taster_name[order(-wineTstr$total)])

#print a plot with the tasters and number of reviews
wineTstr %>% ggplot(aes(x= taster_name, y=total)) + geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_text(aes(label = sprintf("%.f%%", 100*totpcnt), y = total+2000)) +
  labs(x="Wine Taster Name", y="Total Wine Reviews", title="Total Reviews by Wine Taster")
```

```{r}
temp <- wineTstr %>% filter(taster_name != "") %>% head(5)

TopTstrCtry <- wine %>% 
  filter(taster_name %in% temp$taster_name) %>%
  group_by(taster_name, country) %>%
  summarise(total = n())

TopTstrCtry %>% 
  ggplot( aes(x=factor(taster_name, levels = wineTstr$taster_name[order(-wineTstr$total)]), 
              y=factor(country, levels= wineCtry$country[order(wineCtry$total)]), 
              size = total)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(x="Taster", y="Country of Wine Reviewed",title="Countries Reviewed by Top 5 Tasters")
```

```{r}
#remove anonymous wine tasters
wineTstr2 = wineTstr %>% filter(wineTstr$taster_name!="") 

#creating a sample data
sample_d = wine %>%
  filter(wine$country %in% head(wineCtry,4)$country & wine$taster_name %in% head(wineTstr2,4)$taster_name)

dim(sample_d)
colnames(sample_d)
str(sample_d)

```


```{r}

## 75% of the sample size
smp_size <- floor(0.75 * nrow(sample_d))

## converting the sample data to train and test data

train_sam <- sample(seq_len(nrow(sample_d)), size = smp_size)

train <- sample_d[train_sam, ]
test <- sample_d[-train_sam, ]


#creating a model using train dataset
model <- lm(points ~ price,data = train)
summary(model)

#predicting the values using test dataset
pred_val <- predict(model,test)

#finding the error(RMSE)

RMSE(pred = pred_val,obs = test$points,na.rm = T)


```
